Containers and R---the Rockerverse and beyond

### 2019-12-09 manuscript.Rmd
Use vectorised logo instead of rasterised logo if the \titlepage command would be used
update AzureContainers description

- [rocker-win](https://github.com/nuest/rocker-win)
- is possible, only relevant in organisations with an existing Windows Server-based infrastructure, can meet policies then

@@

**AzureContainers** ([https://cran.r-project.org/package=AzureContainers](https://cran.r-project.org/package=AzureContainers))
<!-- From the cran description
 lets you build and deploy containerised services in R, using Docker and Kubernetes. For full functionality, you should have Docker installed, as well as the kubectl and helm commandline tools. Otherwise it is relatively lightweight, requiring neither Powershell nor Python.
-->

@@

\begin{figure}[htbp]
  \centering
  \includegraphics[width=\textwidth]{figures/liftr-workflow}
  \caption{The liftr workflow for rendering containerized R Markdown documents.}
  \label{figure:liftr}
\end{figure}

>>>>

- [rocker-win](https://github.com/nuest/rocker-win)
- is possible, only relevant in organisations with an existing Windows Server-based infrastructure, can meet policies then
<!-- can also be relevant for standalone Win 10 Professional users who have Docker for Windows installed -- HO -->

@@

**AzureContainers** ([https://cran.r-project.org/package=AzureContainers](https://cran.r-project.org/package=AzureContainers)) is an interface to a number of container-related services in Microsoft's Azure cloud, namely Container Instances, Container Registry and Kubernetes Service. While it is mainly intended for working with Azure, as a convenience feature it includes lightweight, cross-platform shells to Docker, kubectl and helm. These can be used to create and manage arbitrary Docker images and containers, as well as Kubernetes clusters on any platform or cloud service.

@@

\begin{figure}[htbp]
  \centering
  \includegraphics[width=\textwidth]{liftr-workflow}
  \caption{The liftr workflow for rendering containerized R Markdown documents.}
  \label{figure:liftr}
\end{figure}
